Kyoto VR MQP Paper First Draft

### 2019-09-20 paper.tex
replace izi.travel image
Replaced the old screenshot of the izi.TRAVEL app because it was full of
JPG artifacts
working on adobe xd design discussion

As we have said, AR is a new and growing field full of opportunities. But of course,
as with anything new, our understanding of AR and how to develop for it is limited.
And with those limitations come challenges. All sorts of different challenges and
limitations face the development and production of AR apps. Here are some that
we considered when working on our app.

@@

By using GPS data from the user's phone to play audio and display images at
specific places in the real world izi.TRAVEL uses a limited form of augmented
reality. Our group aimed to implement and extend this functionality in our own
app. See Section \ref{sec:aruku} for more details.

@@

\subsection{ARuku}
\label{sec:aruku}

>>>>

As previously discussed, AR is a new and growing field full of opportunities.
But of course, as with anything new, our understanding of AR and how to develop
for it is limited.  And with those limitations come challenges. All sorts of
    different challenges and limitations face the development and production of
    AR apps. Here are some that we considered when working on our app.

@@

By using GPS data from the user's phone to play audio and display images at
specific places in the real world izi.TRAVEL uses a limited form of augmented
reality. Our group aimed to implement and extend this functionality in our own
app. See Section \ref{sec:aruko} for more details.

@@

\subsection{ARuko}
\label{sec:aruko}

\subsubsection{Adobe XD Design}
\label{sec:aruko}
On September 10th, Atticus Sims presented us with a storyboard for the app
experience. We would not be able to resume work until September 17th due to
prior travel plans. Whether Atticus knew this or not, the design he put forth
had ramifications that rippled throughout the entire software stack we had
constructed up to this point. Figure~\ref{fig:adobeXdDesign} shows this design.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{adobe-xd-design.png}
	\caption[A screenshot of the Adobe XD project designed by Atticus Sims]
    {A screenshot of the Adobe XD project designed by Atticus Sims}
	\label{fig:adobeXdDesign}
\end{figure}

One of the notable changes is the chapter select screen, which is the third
screen in Figure~{fig:adobeXdDesign}. Before, we worked under the assumption
that each geolocation-triggered region would not have to be ordered in any way.
This assumption made its way into Editour, which did not currently have a way
to reorder regions once they were placed. Because of this chapter selection
screen, we needed some way to rearrange the order of regions within Editour.

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
to place images onto the ground-plane using the AR camera. Instead, he
suggested that we have the images be viewable in a more traditional
fashion---in 2D as part of the UI. This was disappointing to us, since we spent
a great deal of effort projecting images into the 3D world using the AR camera;
we felt like we figured out how to use this technology in a way that was both
usable and fun. Ideally, we wanted to explore ways to theme the 2D images in
the 3D world, such as by framing the images in a traditional Japanese pagoda,
which would fit in with the environment. On the same screen, there is a
scrollable window of text for a transcript of the audio. Because of this, the
Editour UI and tour metadata JSON file needed to be updated to accomodate a
transcript per region. On top of this, the C\# code that interprets the tour
file needed to be updated to expect an audio transcript field.
Figure~\ref{fig:editourAdditions} shows the UI elements that changed in order
to add these new features. The arrows next to the region name can be used to
move the "Region Card" up and down in the side bar. In the "Media" tab, there
is also a text area to include a transcript of the uploaded audio file.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption[Additions to the editour to accommodate the new design]
    {Additions to the editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

In Editour, the frontend alone was already around three thousand lines of
vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc made
the growing code complexity more manageable. Excluding Node modules, the only
external library we used for Editour was Leaflet, an open-source JavaScript
library for interactive maps \autocite{leafletjs}. We did not use any libraries
for developing frontends like Facebook's React or Google's Angular. Instead,
all of the complex UI interactions were handled by modifying the DOM directly
with JavaScript's built-in functionality. Furthermore, we did not use any
advanced frontend build tools such as Rollup, webpack or Parcel. This was
likely an appropriate decision for a JavaScript project of this scope, but if
we were to continue to develop Editour, UI libraries and frontend build tools
would be something to consider.

With the ground-plane detection features stripped away from the main app, the
AR focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
Atticus took photographs of various signs throughout Kinkakuji for us to use as
image targets. In this design, the AR camera superimposes an "info" button on
top of the sign. Tapping on this button brings up a separate UI element
containing the translation, which can be seen in Figure~\ref{fig:signTranslation}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{sign-translation.png}
	\caption[Additions to the editour to accommodate the new design]
    {Additions to the editour to accommodate the new design}
	\label{fig:signTranslation}
\end{figure}

ordering*
transcripts*
no more ground plane detection*
many, many image targets
thumbnails for the chapter
